Output Summary

### 2020-11-19 03-post-process/output-plots.Rmd
Updates to output plots Rmd source
* drop deleted parameter from diagnostics: phi_Mb_M
* Add a fit plot for survival of hatchery fish to LGD
* Recalculate  SARS to be from LGD to trib

```{r mcmc-diags}
# groups of parameters to match and calculate diagnostic summaries for separately
diag_params = list(
  c("alpha", "beta", "sigma_Pb"),
  "gamma",
  "^mu_phi",
  "^mu_psi",
  "^mu_omega",
  "^mu_pi",
  "^sig_Lphi",
  "^sig_Lpsi",
  c("^sig_Lomega", "^sig_Lpi"),
  "^Pb[", 
  "init_recruits", 
  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]",
  "^phi_Mb_M["
)

@@

```{r survival-data-fits, fig.width = 3, fig.height = 5}
par(mfcol = c(3,1), oma = c(1.5,1.5,0,0))

plot_tseries(post_summ(post, "^phi_Pb_Ma["), expit(jags_data$Lphi_obs_Pb_Ma[observable]), main = "Summer Tagging to LGD")
plot_tseries(post_summ(post, "^phi_Pa_Ma[.+,1]$"), expit(jags_data$Lphi_obs_Pa_Ma[observable,1]), main = "Fall Trap to LGD")
plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2]), main = "Spring Trap to LGD")
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

This is survival from $Mb$ (smolts in tributary, prior to mortality associated with movement to LGD) to $Ra$ (adults returning to tributary, vulnerable to being counted at weir).

@@

Other SARS could be calculated, but currently this is the only one that is comparable between hatchery and natural origins.

```{r sar-plot}
# function to calculate posterior 
get_SAR_post = function(post, jags_data) {
  # extract posterior abundances
  Ra_post = post_subset(post, "^Ra[", T) # adults returning to tributary
  Mb_post = post_subset(post, "^Mb[", T) # smolts leaving tributary in spring

@@

  # loop over mcmc iters
  for (i in 1:ni) {
    # extract quantities for this iter
    Ra = array_format(Ra_post[i,])
    Mb = array_format(Mb_post[i,])

    # give names
    dimnames(Ra) = dimnames(jags_data$p_remove)
    dimnames(Mb) = dimnames(jags_data$Mb_obs)

@@

    # loop over years
    nat_SAR_i = hat_SAR_i = NULL
    for (y in first_SAR_y:last_SAR_y) {
      # sum up smolts across life history types
      nat_smolt = sum(Mb[y,,"Nat"])
      hat_smolt = sum(Mb[y,,"Hat"], na.rm = T)

      # sum up returing adults from this brood
      nat_adults = Ra[y+3,1,"Nat"] + Ra[y+4,2,"Nat"] + Ra[y+5,3,"Nat"]
      hat_adults = Ra[y+3,1,"Hat"] + Ra[y+4,2,"Hat"] + Ra[y+5,3,"Hat"]

@@

* `mu_omega[1]`: mean probability of being a female at ocean entry
* `mu_phi_Ma_M`: mean probability of surviving from LGD to ocean entry
* `mu_phi_Mb_M`: mean probability of surviving from hatchery release in spring to estuary (hatchery fish)
* `mu_phi_Mb_Ma`: mean probability of surviving movement from tributary to LGD (same for both LH types)
* `mu_phi_Pa_Mb`: mean probability of surviving overwinter in tributary (`[1]`: fall migrants, `[2]`: spring migrants)
* `mu_pi[1]`: mean probability of becoming a fall migrant LH type at end of summer
* `mu_psi_O1_Rb`: mean probability of maturing at age 3 given survived to that point (`[1]`: females, `[2]`: males)
* `mu_psi_O2_Rb`: mean probability of maturing at age 4 given did not mature at age 3 and survived to that point (`[1]`: females, `[2]`: males)

>>>>

```{r mcmc-diags}
# groups of parameters to match and calculate diagnostic summaries for separately
diag_params = list(
  c("alpha", "beta", "sigma_Pb"),
  "gamma",
  "^mu_phi",
  "^mu_psi",
  "^mu_omega",
  "^mu_pi",
  "^sig_Lphi",
  "^sig_Lpsi",
  c("^sig_Lomega", "^sig_Lpi"),
  "^Pb[", 
  "init_recruits", 
  "^phi_Ma_M", "^phi_Mb_Ma[.+,2]", "^phi_Pa_Mb[.+,1]", "^phi_Pa_Mb[.+,2]"
)

@@

```{r survival-data-fits, fig.width = 3, fig.height = 6}
par(mfcol = c(4,1), oma = c(1.5,1.5,0,0))

plot_tseries(post_summ(post, "^phi_Pb_Ma["), expit(jags_data$Lphi_obs_Pb_Ma[observable]), main = "(Nat) Summer Tagging to LGD")
plot_tseries(post_summ(post, "^phi_Pa_Ma[.+,1]$"), expit(jags_data$Lphi_obs_Pa_Ma[observable,1]), main = "(Nat) Fall Trap to LGD")
plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,1]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,1]), main = "(Nat) Spring Trap to LGD")
plot_tseries(post_summ(post, "^phi_Mb_Ma[.+,2,2]$"), expit(jags_data$Lphi_obs_Mb_Ma[observable,2,2]), main = "(Hat) Spring Release to LGD")
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Survival")
```

@@

This is survival from $Ma$ (smolts at the top of LGD) to $Ra$ (adults returning to tributary, vulnerable to being counted at weir).

@@

```{r sar-plot}
# function to calculate posterior 
get_SAR_post = function(post, jags_data) {
  # extract posterior abundances
  Ra_post = post_subset(post, "^Ra[", T) # adults returning to Columbia River mouth
  Ma_post = post_subset(post, "^Ma[", T) # smolts at top of LGD

@@

  # loop over mcmc iters
  for (i in 1:ni) {
    # extract quantities for this iter
    Ra = array_format(Ra_post[i,])
    Ma = array_format(Ma_post[i,])

    # give names
    dimnames(Ra) = dimnames(jags_data$p_remove)
    dimnames(Ma) = dimnames(jags_data$Mb_obs)

@@

    # loop over years
    nat_SAR_i = hat_SAR_i = NULL
    for (y in first_SAR_y:last_SAR_y) {
      # sum up smolts across life history types
      nat_smolt = sum(Ma[y,,"Nat"])
      hat_smolt = sum(Ma[y,,"Hat"])

      # sum up returning adults from this brood
      nat_adults = Ra[y+3,1,"Nat"] + Ra[y+4,2,"Nat"] + Ra[y+5,3,"Nat"]
      hat_adults = Ra[y+3,1,"Hat"] + Ra[y+4,2,"Hat"] + Ra[y+5,3,"Hat"]

@@

* `mu_omega[1]`: mean probability of being a female at ocean entry
* `mu_phi_Ma_M`: mean probability of surviving from LGD to ocean entry
* `mu_phi_Mb_Ma`: mean probability of surviving movement from tributary to LGD (same for both LH types, different for origin types)
* `mu_phi_Pa_Mb`: mean probability of surviving overwinter in tributary (`[1]`: fall migrants, `[2]`: spring migrants)
* `mu_pi[1]`: mean probability of becoming a fall migrant LH type at end of summer
* `mu_psi_O1_Rb`: mean probability of maturing at age 3 given survived to that point (`[1]`: females, `[2]`: males)
* `mu_psi_O2_Rb`: mean probability of maturing at age 4 given did not mature at age 3 and survived to that point (`[1]`: females, `[2]`: males)
